Comments on Blair and Sambanis, 2020, \"Forecasting Civil Wars: Theory and Structure in an Age of 'Big Data' and Machine Learning\", *JCR*

### 2020-06-10 paper.Rmd
fixed table 4
I messed up table 4 in my last commit... my bad

The most straightforward method of incorporating the annual structural PITF variables--adding them to the predictors of the Escalation RF model--strictly outperforms the Escalation Only model. Note that the two other combination models considered are both non-standard and that the "PITF Split Population" model does not incorporate structural information at all. We thus conclude that adding structural variables improves predictive performance.

@@

tab4o <- tab4o %>%
  rename(header = type) %>%
  mutate(source = "Original, scored with civil war incidence")
tab4f <- tab4f %>%
  rename(`Predicted 0` = `0`, `Predicted 1` = `1`) %>%
  mutate(source = "Fixed, scored with civil war onset")

>>>>

The most straightforward method of incorporating the annual structural PITF variables---adding them to the predictors of the Escalation RF model---strictly outperforms the Escalation Only model. Note that the two other combination models considered are both non-standard and that the "PITF Split Population" model does not incorporate structural information at all. We thus conclude that adding structural variables improves predictive performance.

@@

tab4o <- tab4o %>%
  rename(header = type) %>%
  mutate(source = "Original, scored with civil war incidence")
tab4f <- tab4f %>%
  rename(Predicted0 = `0`, Predicted1 = `1`) %>%
  mutate(source = "Fixed, scored with civil war onset")
